$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-11 paper/e6ssm-tuning-paper.tex

>>>>

The extra $U(1)^\prime$ gauge symmetry may mix with the $U(1)_Y$ gauge
symmetry associated with hypercharge through gauge kinetic mixing,
\be
\mathcal{L}_{mix}^{kin}=-\frac{\sin\chi}{2}F^{Y}_{\mu\nu}F^{N}_{\mu\nu}\,.
\label{Eq:GKM}
\ee
where  $F_{\mu\nu}^Y$ and $F_{\mu\nu}^{N}$ are field strengths associated with the
$U(1)_Y$ and $U(1)_{N}$ respectively. The gauge kinetic mixing can have a significant impact on the phenomenology \cite{Rizzo:1998ut,Salvioni:2009mt,Krauss:2012ku}, which may in particular reduce the $Z^\prime$ limit mass by up to $200$ GeV.

However if the extra $U(1)$ gauge symmetries appears from the breakdown of $E_6$, then $\sin\chi$ should be zero at the GUT scale. Nonetheless even if this term is zero at the outset it will still be radiatively generated if the trace of their charges, $\sum_i Q_i^Y Q^\prime_i$, is non-zero.  In the cases studied here the trace of the charges over states in the complete $27$-plets vanish, but to be consistent with single step gauge coupling unification we also included $\hat{H}^\prime$ and $\hat{\overline{H^\prime}}$ which lead to a non-zero value for $\sum_i Q_i^Y Q^\prime_i $.  The value induced by this at the EW scale though is rather small as can be seen \footnote{The specific incomplete multiplets we consider here correspond to the third of the four possible embeddings they refer to.} in Fig.~3 of \cite{Rizzo:1998ut}, and this was also checked with two-loop RGEs in the E$_6$SSM \cite{King:2005jy,Athron:2009bs}.  For this reason and due to the huge expansion in the number of terms in the two-loop RGEs when one allows for gauge kinetic mixing we will neglect this in our analysis here and throughout this paper.

In general though it is possible for gauge kinetic mixing to be much larger as can be the case if one considers an additional $5 + \overline{5}$ pair of SU(5) multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case this will  impact the results in two ways, firstly by altering the $Z^\prime$ limit from experiment and secondly by altering the charges which appear in the EWSB condition, which can be ween from examining Eqs.~\ref{eq:originalE6MZequation}-\ref{eq:ddefn}.
